---
title: "R Notebook"
output: html_notebook
---

# Load in libraries for classification and EDA
```{r}
library(caret)
library(dplyr)
#install.packages("corrplot")
library(corrplot)
library(ggplot2)
#install.packages("naivebayes")
library(naivebayes)
#install.packages("sgd")
library(sgd)
library(class)
#install.packages("tree")
library(tree)
library(randomForest)
library(e1071)
#install.packages("psych")
library(psych)
#install.packages("plotmo")
library(plotmo)
```

Load in data set
```{r}
dna0 <- read.csv("codon_usage.csv")
summary(dna0)
str(dna0)
```

Change first two codons to numeric data type by dropping character rows
```{r}
dna1 <- dna0

dna1[grep("^non", dna1$UUU), ] <- NA
dna1[grep("-", dna1$UUC), ] <- NA

dna1$DNAtype <- as.factor(dna1$DNAtype)
dna1$UUU <- as.numeric(dna1$UUU)
dna1$UUC <- as.numeric(dna1$UUC)
dna1$Kingdom <- as.factor(dna1$Kingdom)

summary(dna1)

dna1 <- na.omit(dna1)

summary(dna1)
```

```{r}
describe(dna1)
```


## Group by Amino Acid
```{r}
dna2 <- dna1

dna2$Phenylalanine <- dna1 %>%
  select(c(UUU, UUC)) %>%
  rowSums()

dna2$Leucine <- dna1 %>% 
  select(c(UUA, UUG, CUU, CUC, CUA, CUG)) %>%
  rowSums()

dna2$Isoleucine <- dna1 %>%
  select(c(AUU, AUC, AUA)) %>%
  rowSums()

dna2$Methionine <- dna1 %>% 
  select(c(AUG)) %>%
  rowSums()

dna2$Valine <- dna1 %>%
  select(c(GUU, GUC, GUA, GUG)) %>%
  rowSums()

dna2$Serine <- dna1 %>%
  select(c(UCU, UCC, UCA, UCG, AGU, AGC)) %>%
  rowSums()

dna2$Proline <- dna1 %>%
  select(c(CCU, CCC, CCA, CCG)) %>%
  rowSums()

dna2$Threonine <- dna1 %>%
  select(c(ACU, ACC, ACA, ACG)) %>%
  rowSums()

dna2$Alanine <- dna1 %>%
  select(c(GCU, GCC, GCA, GCG)) %>%
  rowSums()

dna2$Tyrosine <- dna1 %>%
  select(c(UAU, UAC)) %>%
  rowSums()

dna2$Stop <- dna1 %>%
  select(c(UAA, UAG, UGA)) %>%
  rowSums()

dna2$Histidine <- dna1 %>%
  select(c(CAU, CAC)) %>%
  rowSums()

dna2$Glutamine <- dna1 %>%
  select(c(CAA, CAG)) %>%
  rowSums()

dna2$Asparagine <- dna1 %>%
  select(c(AAU, AAC)) %>%
  rowSums()

dna2$Lysine <- dna1 %>%
  select(c(AAA, AAG)) %>%
  rowSums()

dna2$Aspartic.acid <- dna1 %>%
  select(c(GAU, GAC)) %>%
  rowSums()

dna2$Glutamic.acid <- dna1 %>%
  select(c(GAA, GAG)) %>%
  rowSums()

dna2$Cysteine <- dna1 %>%
  select(c(UGU, UGC)) %>%
  rowSums()

dna2$Tryptophan <- dna1 %>%
  select(c(UGG)) %>%
  rowSums()

dna2$Arginine <- dna1 %>%
  select(c(CGU, CGC, CGA, CGG, AGA, AGG)) %>%
  rowSums()

dna2$Glycine <- dna1 %>%
  select(c(GGU, GGC, GGA, GGG)) %>%
  rowSums()
```

## Group by biochemical properties
```{r}
dna2$Nonpolar <- dna2 %>%
  select(c(Phenylalanine, Leucine, Isoleucine, Methionine, Valine, Proline, Alanine, Tryptophan, Glycine)) %>%
  rowSums()

dna2$Polar <- dna2 %>%
  select(c(Serine, Threonine, Tyrosine, Glutamine, Asparagine, Cysteine)) %>%
  rowSums()

dna2$Basic <- dna2 %>%
  select(c(Histidine, Lysine, Arginine)) %>%
  rowSums()

dna2$Acidic <- dna2 %>%
  select(c(Aspartic.acid, Glutamic.acid)) %>%
  rowSums()
```

```{r}
dna.aa <- dna2 %>%
  select(c(Kingdom, Phenylalanine, Leucine, Isoleucine, Methionine, Valine, Proline, Alanine, Tryptophan, Glycine,
           Serine, Threonine, Tyrosine, Glutamine, Asparagine, Cysteine, Histidine, Lysine, Arginine, 
           Aspartic.acid, Glutamic.acid, Stop))

dna.bio <- dna2 %>%
  select(c(Kingdom, Nonpolar, Polar, Basic, Acidic))
```

## EDA
```{r}
ggplot(dna1, aes(x = Kingdom, y = ..count.., fill = DNAtype)) + 
  geom_bar()

ggplot(dna1, aes(x = UUU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UUC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UUA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UUG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CUU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CUC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CUA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CUG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AUU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AUC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AUA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AUG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GUU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GUC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GUA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GUG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GCU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GCC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GCA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GCG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CCU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CCC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CCA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CCG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UGG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GGU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GGC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GGA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GGG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UCU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UCC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UCA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UCG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AGU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AGC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = ACU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = ACC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = ACA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = ACG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UAU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UAC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CAA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CAG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AAU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AAC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UGU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CAU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CAC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AAA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CGU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CGC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CGA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = CGG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AGA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = AGG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GAU, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GAC, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GAA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = GAG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UAA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UAG, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))

ggplot(dna1, aes(x = UGA, y = Kingdom)) + 
  geom_point(aes(color = DNAtype))
```
## Partition the data into three sections Codons, Amino Acids, Biochemical Properties
```{r}
dna1 <- dna1 %>%
  select(-c(DNAtype, SpeciesID, Ncodons,SpeciesName))

set.seed(175)
controlObject <- trainControl(method = "repeatedcv", number = 10, repeats = 5)

forTraining <- createDataPartition(dna1$Kingdom, p = 0.8, list = FALSE)
dna.train <- dna1[forTraining, ]
dna.test <- dna1[-forTraining, ]

forTraining.aa <- createDataPartition(dna.aa$Kingdom, p = 0.8, list = FALSE)
dna.aa.train <- dna.aa[forTraining.aa, ]
dna.aa.test <- dna.aa[-forTraining.aa, ]

forTraining.bio <- createDataPartition(dna.bio$Kingdom, p = 0.8, list = FALSE)
dna.bio.train <- dna.bio[forTraining.bio, ]
dna.bio.test <- dna.bio[-forTraining.bio, ]
```

Correlation Matrix
```{r}
dna2.codon.cor <- dna1 %>%
  select(!c(Kingdom)) %>%
  cor()
corrplot(dna2.codon.cor, method = 'color', order = 'FPC', type = 'lower', tl.cex = 0.5)

dna2.aa.cor <- dna2 %>%
  select(c(Phenylalanine, Leucine, Isoleucine, Methionine, Valine, Serine, Proline, Threonine,
           Alanine, Tyrosine, Stop, Histidine, Glutamine, Asparagine, Lysine, Aspartic.acid,
           Glutamic.acid, Cysteine, Tryptophan, Arginine, Glycine)) %>%
  cor()
corrplot(dna2.aa.cor, method = 'color', order = 'FPC', type = 'lower')

dna2.bio.cor <- dna2 %>%
  select(c(Nonpolar, Polar, Basic, Acidic)) %>%
  cor()
corrplot(dna2.bio.cor, method = 'color', order = 'FPC', type = 'lower')
```
```{r}
dna1.pca <- prcomp(dna1[, c(6:65)], center = TRUE, scale. = TRUE)

summary(dna1.pca)

plot(dna1.pca)
```

```{r}
dna1.pca.sub1 <- dna1 %>%
  select(c(GGC, GUC, CUG, GCC, GAC, CGC, CCG, GCG, GUG, CGG, CAG, GAG, ACG, UCG, ACC, AGC, CAC, CCC, CUC, UAC, AUC, UCC, AAC, UUC, UGC, AAG, GGG, UGG, AUG, AGG, UAG))

dna1.pca1 <- prcomp(dna1.pca.sub1, center = TRUE, scale. = TRUE)

summary(dna1.pca1)

plot(dna1.pca1)
```

```{r}
dna1.pca.sub2 <- dna1 %>% 
  select(-c(GGC, GUC, CUG, GCC, GAC, CGC, CCG, GCG, GUG, CGG, CAG, GAG, ACG, UCG, ACC, AGC, CAC, CCC, CUC, UAC, AUC, UCC, AAC, UUC, UGC, AAG, GGG, UGG, AUG, AGG, UAG, Kingdom))

dna1.pca2 <- prcomp(dna1.pca.sub2, center = TRUE, scale. = TRUE)

summary(dna1.pca2)

plot(dna1.pca2)
```

## Linear Discriminant Analysis
```{r}
dna.lda <- train(Kingdom ~ ., data = dna.train, 
                 method = "lda", preProc = c("center", "scale"), trControl = controlObject)

dna.lda
```

### Check Variable Importance on trained model
```{r}
dna.lda$finalModel

varImp(dna.lda)

plot(varImp(dna.lda))
```
### Calculate Accuracy and Kappa for Test Data
```{r}
dna.lda.pred <- predict(dna.lda, dna.test)

dna.lda.test <- data.frame(obs = dna.test$Kingdom, pred = dna.lda.pred)

dna.lda.stats <- defaultSummary(dna.lda.test)

dna.lda.stats
```

## Naïve Bayes
```{r}
dna.nb <- train(Kingdom ~ ., data = dna.train, method = "naive_bayes", preProc = c("center", "scale"), 
                trControl = controlObject)

dna.nb

plot(dna.nb)

varImp(dna.nb)

plot(varImp(dna.nb))
```

```{r}
dna.nb.pred <- predict(dna.nb, dna.test)

dna.nb.test <- data.frame(obs = dna.test$Kingdom, pred = dna.nb.pred)

dna.nb.stats <- defaultSummary(dna.nb.test)

dna.nb.stats
```


## Stochastic Gradient Descent
```{r}
# gbmGrid <- expand.grid(.interaction.depth = seq(1, 7, by = 2), .n.trees = seq(100, 1000, by = 50),
#                       .shrinkage = c(.001, .1), .n.minobsinnode = 10)

dna.sgd <- train(Kingdom ~ ., data = dna.train, method = "gbm", verbose = FALSE, 
                trControl = controlObject)

summary(dna.sgd)
```

## K-Nearest Neighbors
```{r}
dna.knn <- train(Kingdom ~ ., data = dna.train, method = "knn", trControl = controlObject)

dna.knn

plot(dna.knn)

varImp(dna.knn)

plot(varImp(dna.knn))
```

```{r}
dna.knn.pred <- predict(dna.knn, dna.test)

dna.knn.test <- data.frame(obs = dna.test$Kingdom, pred = dna.knn.pred)

dna.knn.stats <- defaultSummary(dna.knn.test)

dna.knn.stats
```


## Decision Tree
```{r}
dna.tree <- train(Kingdom ~ ., data = dna.train, method = "rpart", trControl = controlObject)

dna.tree

plot(dna.tree)

varImp(dna.tree)

plot(varImp(dna.tree))
```

```{r}
dna.tree.pred <- predict(dna.tree, dna.test)

dna.tree.test <- data.frame(obs = dna.test$Kingdom, pred = dna.tree.pred)

dna.tree.stats <- defaultSummary(dna.tree.test)

dna.tree.stats
```


## Random Forest
```{r}
dna.rf <- train(Kingdom ~ ., data = dna.train, method = "rf", importance = TRUE)

dna.rf

plot(dna.rf)

varImp(dna.rf)

plot(varImp(dna.rf))
```

```{r}
dna.rf.pred <- predict(dna.rf, dna.test)

dna.rf.test <- data.frame(obs = dna.test$Kingdom, pred = dna.rf.pred)

dna.rf.stats <- defaultSummary(dna.rf.test)

dna.rf.stats
```

## SVM
```{r}
dna.svm <- train(Kingdom ~ ., data = dna.train, method = "svmRadial")

dna.svm

plot(dna.svm)

varImp(dna.svm)

plot(varImp(dna.svm))
```

```{r}
dna.svm.pred <- predict(dna.svm, dna.test)

dna.svm.test <- data.frame(obs = dna.test$Kingdom, pred = dna.svm.pred)

dna.svm.stats <- defaultSummary(dna.svm.test)

dna.svm.stats
```

# Amino Acid Models

## Linear Discriminant Analysis
```{r}
dna.aa.lda <- train(Kingdom ~ ., data = dna.aa.train, 
                 method = "lda", preProc = c("center", "scale"), trControl = controlObject)

dna.aa.lda
```

### Check Variable Importance on trained model
```{r}
dna.aa.lda$finalModel

varImp(dna.aa.lda)

plot(varImp(dna.aa.lda))
```

### Calculate Accuracy and Kappa for Test Data
```{r}
dna.aa.lda.pred <- predict(dna.aa.lda, dna.aa.test)

dna.aa.lda.test <- data.frame(obs = dna.aa.test$Kingdom, pred = dna.aa.lda.pred)

dna.aa.lda.stats <- defaultSummary(dna.aa.lda.test)

dna.aa.lda.stats
```

## Naïve Bayes
```{r}
dna.aa.nb <- train(Kingdom ~ ., data = dna.aa.train, method = "naive_bayes", preProc = c("center", "scale"), 
                trControl = controlObject)

dna.aa.nb

plot(dna.aa.nb)

varImp(dna.aa.nb)

plot(varImp(dna.aa.nb))
```

```{r}
dna.aa.nb.pred <- predict(dna.aa.nb, dna.aa.test)

dna.aa.nb.test <- data.frame(obs = dna.aa.test$Kingdom, pred = dna.aa.nb.pred)

dna.aa.nb.stats <- defaultSummary(dna.aa.nb.test)

dna.aa.nb.stats
```

## K-Nearest Neighbors
```{r}
dna.aa.knn <- train(Kingdom ~ ., data = dna.aa.train, method = "knn", trControl = controlObject)

dna.aa.knn

plot(dna.aa.knn)

varImp(dna.aa.knn)

plot(varImp(dna.aa.knn))
```

```{r}
dna.aa.knn.pred <- predict(dna.aa.knn, dna.aa.test)

dna.aa.knn.test <- data.frame(obs = dna.aa.test$Kingdom, pred = dna.aa.knn.pred)

dna.aa.knn.stats <- defaultSummary(dna.aa.knn.test)

dna.aa.knn.stats
```

## Decision Tree
```{r}
dna.aa.tree <- train(Kingdom ~ ., data = dna.aa.train, method = "rpart", trControl = controlObject)

dna.aa.tree

plot(dna.aa.tree)

varImp(dna.aa.tree)

plot(varImp(dna.aa.tree))
```

```{r}
dna.aa.tree.pred <- predict(dna.aa.tree, dna.aa.test)

dna.aa.tree.test <- data.frame(obs = dna.aa.test$Kingdom, pred = dna.aa.tree.pred)

dna.aa.tree.stats <- defaultSummary(dna.aa.tree.test)

dna.aa.tree.stats
```


## Random Forest
```{r}
dna.aa.rf <- train(Kingdom ~ ., data = dna.aa.train, method = "rf", importance = TRUE)

dna.aa.rf

plot(dna.aa.rf)

varImp(dna.aa.rf)

plot(varImp(dna.aa.rf))
```

```{r}
dna.aa.rf.pred <- predict(dna.aa.rf, dna.aa.test)

dna.aa.rf.test <- data.frame(obs = dna.aa.test$Kingdom, pred = dna.aa.rf.pred)

dna.aa.rf.stats <- defaultSummary(dna.aa.rf.test)

dna.aa.rf.stats
```

## SVM
```{r}
dna.aa.svm <- train(Kingdom ~ ., data = dna.aa.train, method = "svmRadial")

dna.aa.svm

plot(dna.aa.svm)

varImp(dna.aa.svm)

plot(varImp(dna.aa.svm))
```

```{r}
dna.aa.svm.pred <- predict(dna.aa.svm, dna.aa.test)

dna.aa.svm.test <- data.frame(obs = dna.aa.test$Kingdom, pred = dna.aa.svm.pred)

dna.aa.svm.stats <- defaultSummary(dna.aa.svm.test)

dna.aa.svm.stats
```

# Biochemical Models

## Linear Discriminant Analysis
```{r}
dna.bio.lda <- train(Kingdom ~ ., data = dna.bio.train, 
                 method = "lda", preProc = c("center", "scale"), trControl = controlObject)

dna.bio.lda
```

### Check Variable Importance on trained model
```{r}
dna.bio.lda$finalModel

varImp(dna.bio.lda)

plot(varImp(dna.bio.lda))
```

### Calculate Accuracy and Kappa for Test Data
```{r}
dna.bio.lda.pred <- predict(dna.bio.lda, dna.bio.test)

dna.bio.lda.test <- data.frame(obs = dna.bio.test$Kingdom, pred = dna.bio.lda.pred)

dna.bio.lda.stats <- defaultSummary(dna.bio.lda.test)

dna.bio.lda.stats
```

## Naïve Bayes
```{r}
dna.bio.nb <- train(Kingdom ~ ., data = dna.bio.train, method = "naive_bayes", preProc = c("center", "scale"), 
                trControl = controlObject)

dna.bio.nb

plot(dna.bio.nb)

varImp(dna.bio.nb)

plot(varImp(dna.bio.nb))
```

```{r}
dna.bio.nb.pred <- predict(dna.bio.nb, dna.bio.test)

dna.bio.nb.test <- data.frame(obs = dna.bio.test$Kingdom, pred = dna.bio.nb.pred)

dna.bio.nb.stats <- defaultSummary(dna.bio.nb.test)

dna.bio.nb.stats
```

## K-Nearest Neighbors
```{r}
dna.bio.knn <- train(Kingdom ~ ., data = dna.bio.train, method = "knn", trControl = controlObject)

dna.bio.knn

plot(dna.bio.knn)

varImp(dna.bio.knn)

plot(varImp(dna.bio.knn))
```

```{r}
dna.bio.knn.pred <- predict(dna.bio.knn, dna.bio.test)

dna.bio.knn.test <- data.frame(obs = dna.bio.test$Kingdom, pred = dna.bio.knn.pred)

dna.bio.knn.stats <- defaultSummary(dna.bio.knn.test)

dna.bio.knn.stats
```

## Decision Tree
```{r}
dna.bio.tree <- train(Kingdom ~ ., data = dna.bio.train, method = "rpart", trControl = controlObject)

dna.bio.tree

plot(dna.bio.tree)

varImp(dna.bio.tree)

plot(varImp(dna.bio.tree))
```

```{r}
dna.bio.tree.pred <- predict(dna.bio.tree, dna.bio.test)

dna.bio.tree.test <- data.frame(obs = dna.bio.test$Kingdom, pred = dna.bio.tree.pred)

dna.bio.tree.stats <- defaultSummary(dna.bio.tree.test)

dna.bio.tree.stats
```


## Random Forest
```{r}
dna.bio.rf <- train(Kingdom ~ ., data = dna.bio.train, method = "rf", importance = TRUE)

dna.bio.rf

plot(dna.bio.rf)

varImp(dna.bio.rf)

plot(varImp(dna.bio.rf))
```

```{r}
dna.bio.rf.pred <- predict(dna.bio.rf, dna.bio.test)

dna.bio.rf.test <- data.frame(obs = dna.bio.test$Kingdom, pred = dna.bio.rf.pred)

dna.bio.rf.stats <- defaultSummary(dna.bio.rf.test)

dna.bio.rf.stats
```

## SVM
```{r}
dna.bio.svm <- train(Kingdom ~ ., data = dna.bio.train, method = "svmRadial")

dna.bio.svm

plot(dna.bio.svm)

varImp(dna.bio.svm)

plot(varImp(dna.bio.svm))
```

```{r}
dna.bio.svm.pred <- predict(dna.bio.svm, dna.bio.test)

dna.bio.svm.test <- data.frame(obs = dna.bio.test$Kingdom, pred = dna.bio.svm.pred)

dna.bio.svm.stats <- defaultSummary(dna.bio.svm.test)

dna.bio.svm.stats
```

### Create DataFrame with stats from all models
```{r}
Model <- c("LDA Codon", "LDA Amino Acid", "LDA Biochemical", "Naive Bayes Codon", 
           "Naive Bayes Amino Acid", "Naive Bayes Biochemical", "KNN Codon", 
           "KNN Amino Acid", "KNN Biochemical", "Decision Tree Codon",
           "Decision Tree Amino Acid", "Decision Tree Biochemical", "Random Forest Codon", 
           "Random Forest Amino Acid", "Random Forest Biochemical", "SVM Codon", 
           "SVM Amino Acid", "SVM Biochemical")
Accuracy <- c(dna.lda.stats[1], dna.aa.lda.stats[1], dna.bio.lda.stats[1], dna.nb.stats[1],
              dna.aa.nb.stats[1], dna.bio.nb.stats[1], dna.knn.stats[1], dna.aa.knn.stats[1],
              dna.bio.knn.stats[1], dna.tree.stats[1], dna.aa.tree.stats[1], dna.bio.tree.stats[1],
              dna.rf.stats[1], dna.aa.rf.stats[1], dna.bio.rf.stats[1], dna.svm.stats[1],
              dna.aa.svm.stats[1], dna.bio.svm.stats[1])
Kappa <- c(dna.lda.stats[2], dna.aa.lda.stats[2], dna.bio.lda.stats[2], dna.nb.stats[2],
              dna.aa.nb.stats[2], dna.bio.nb.stats[2], dna.knn.stats[2], dna.aa.knn.stats[2],
              dna.bio.knn.stats[2], dna.tree.stats[2], dna.aa.tree.stats[2], dna.bio.tree.stats[2],
              dna.rf.stats[2], dna.aa.rf.stats[2], dna.bio.rf.stats[2], dna.svm.stats[2],
              dna.aa.svm.stats[2], dna.bio.svm.stats[2])

models <- data.frame(Model, Accuracy, Kappa)

models
```

```{r}
data.frame("Kingdom" = dna.test$Kingdom, "Prediction" = dna.svm.pred, "Compare" = dna.test$Kingdom == dna.svm.pred) %>%
  group_by(Kingdom, Compare) %>%
  summarise(n = n())
```

```{r}
data.frame("Kingdom" = dna.test$Kingdom, "Prediction" = dna.knn.pred, "Compare" = dna.test$Kingdom == dna.knn.pred) %>%
  group_by(Kingdom, Compare) %>%
  summarise(n = n())
```

```{r}
data.frame("Kingdom" = dna.test$Kingdom, "Pred" = dna.rf.pred, "Compare" = dna.test$Kingdom == dna.rf.pred) %>%
  group_by(Kingdom, Compare) %>%
  summarise(n = n())
```

